Analysis on car sale data

### 2021-01-15 paper.Rmd
Add files via upload

@@

>>>>

Cars have become an important component of modern life, and it is one of the most common transportation. Many websites and blogs provide car advice to people who are interested, and these advice covers nearly all aspects of car. However, despite the large amount and wide coverage of these advice, there are no current work on data-based customer advise, and most of the suggestions available online are only based on subjective opinions rather than strict data analysis. Therefore, we decided to contribute this data science project.

@@

Due to the lack of sufficient data, our conclusion may not be guaranteed to be correct when a lot of other car models are introduced. In the future, larger datasets can be used to establish a more general correlation and make our conclusion more solid.
